Software Architectures to Integrate Workflow Engines in Science Gateways

### 2016-04-27 paper.tex
Added a sentence on science gateways that do not include any workflow engine (following @merous' comment)

Science gateways are used to share resources in a community and to
provide increased performance and capacity through facilitated access to storage and
computing power. They are often accessible through a web interface
that helps users manage access rights, data transfers, task execution
and authentication on multiple computing and storage
locations. Workflow engines are part of this ecosystem as core
components to implement and execute applications.

@@

Integration between workflow engines and science gateways varies
across systems. Some science gateways may be tailored to a particular
engine that manages critical functions such as task execution, data
transfers and authentication. Other gateways may be more general and
host applications executed by different types of
engines. Extensibility is an important property of the integration, as
new workflows are added frequently, different types and versions of
workflow engines may be integrated over time, and different kinds of
infrastructure can be targeted.

Scalability is also an important concern, since science gateways are
multi-user systems that manage substantial amounts of data and execute
computationally-intensive analyses. To this end, science gateways
may include different instances of the same engine type and implement
some load-balancing policy among them. They may also use advanced
task scheduling policies on the infrastructure, e.g. to ensure fairness
among users~\cite{FERR-14,CPE:CPE3708} or to improve
fault-tolerance~\cite{wilkins2008teragrid,FERR-13}.

>>>>

Science gateways are used to share resources within a community and to
provide increased performance and capacity through facilitated access
to storage and computing power. They are often accessible through a
web interface that helps users manage access rights, data transfers,
task execution and authentication on multiple computing and storage
locations. Workflow engines are part of this ecosystem as core
components to implement and execute applications.

@@

Integration between workflow engines and science gateways varies
across systems. Some science gateways may be tailored to a particular
engine that manages critical functions such as task execution, data
transfers and authentication. Other gateways may be more general and
host applications executed by different types of engines. Finally,
some science gateways may not use any workflow engine and focus on the
execution of simple tasks -- this class of systems is not covered by
our analysis.

Extensibility is an important property of the integration, as new
workflows are added frequently, different types and versions of
workflow engines may be integrated over time, and different kinds of
infrastructure can be targeted.

Scalability is also a crucial concern, since science gateways are
multi-user systems that manage substantial amounts of data and execute
computationally-intensive analyses. To this end, science gateways
may include different instances of the same engine type and implement
some load-balancing policy among them. They may also use advanced
task scheduling policies on the infrastructure, e.g. to ensure fairness
among users~\cite{FERR-14,CPE:CPE3708} or to improve
fault-tolerance~\cite{wilkins2008teragrid,FERR-13}.
